EuringPosterFigures

### 2021-04-28 scripts/EuringPosterFigures.Rmd
case study figures added, changed color palette to something bolder

>>>>

#filter to see that adult survival bias does in fact vary with L/M/H detection
ggplot(phiad.plot.vals %>% filter(variable == 'Adult survival'), 
       aes(x = factor(phiad_cat), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True Adult survival') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative bias",
                      mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,
                      breaks = c(-0.5, -0.25, 0, 0.25, 0.5), n.breaks = 5, 
                      labels = c('0.5', "-0.25", "0", "0.25", '0.5')) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        axis.text.x = element_text(angle = 90, vjust = 0.5))
